openarchaeoCollaboration

### 2022-04-25 analysis/paper.Rmd
Initial network analysis
Including repo-user and repo-repo graphs

```{r dependencies, include=FALSE}
library("tidyverse")
library("lubridate")
library("openarchaeoCollaboration")
library("khroma")
library("gt")
library("fs")
library("here")
```

@@

>>>>

```{r dependencies, include=FALSE}
library("tidyverse")
library("lubridate")
library("openarchaeoCollaboration")
library("khroma")
library("gt")
library("fs")
library("here")
library("tidygraph")
library("ggraph")
```

@@

To construct our graphs we need a table linking users to repos by collaborative activity.
For this purpose commits, issues, and comments are all considered contributions.

```{r graph-data}
oarch |>
  drop_na(gh_repo) |>
  nest(tags = c(tag1, tag2, tag3, tag4, tag5)) |>
  select(gh_repo, category, tags, gh_commits, gh_issues, gh_comments) ->
  oarch_graph

oarch_graph <- bind_rows(
  oarch_graph |>
    unnest(gh_comments) |>
    group_by(repo, author) |>
    summarise(category, tags,
              contrib = "comment", n_contrib = n(), .groups = "drop"),
  oarch_graph |>
    unnest(gh_issues) |>
    group_by(repo, author) |>
    summarise(category, tags,
              contrib = "issue", n_contrib = n(), .groups = "drop"),
  oarch_graph |>
    unnest(gh_commits) |>
    group_by(repo, author) |>
    summarise(category, tags,
              contrib = "commit", n_contrib = n(), .groups = "drop")
)

oarch_graph <- rename(oarch_graph, user = author)
```

With this, we can construct our three graphs: repo–user, repo–repo (by common users), and user–user (by common repos).

### Repo–user

```{r plot-graph-repo-user}
oarch_graph |>
  pivot_longer(c(repo, user), names_to = "node_type", values_to = "node") |>
  select(node, node_type) |>
  distinct() ->
  nodes

oarch_graph |>
  rename(to = repo, from = user) ->
  edges

tbl_graph(nodes, edges) |>
  ggraph(layout = "graphopt") +
  geom_edge_fan(aes(colour = contrib, alpha = n_contrib)) +
  geom_node_point(aes(colour = node_type)) +
  scale_edge_alpha(trans = "log")
```

### Repo–repo

```{r plot-graph-repo-repo}
oarch_graph |>
  select(repo, category) |>
  distinct() ->
  nodes

oarch_graph |>
  left_join(oarch_graph, by = "user") |>
  select(repo.x, user, repo.y) |>
  filter(repo.x != repo.y) |>
  filter(!str_detect(user, coll("[bot]"))) |>
  distinct() |>
  count(repo.x, repo.y) |>
  rename(to = repo.x, from = repo.y) ->
  edges

tbl_graph(nodes, edges) |>
  ggraph(layout = "graphopt") +
  geom_edge_fan(aes(alpha = n)) +
  geom_node_point(aes(colour = category)) +
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common contributors")
```

### User–user

```{r plot-graph-repo-user}
# TODO
```
